Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-08-31 paper.tex
no message

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

\usepackage{url}
\urldef{\mailsa}\path|{yilmaz.onur, karagoz,}@metu.edu.tr|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Computer Engineering Deperatment, Middle East Technical University, Turkey
\mailsa\\

@@

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle

>>>>

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{url}
\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|  
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Computer Engineering Deperatment, Middle East Technical University, Turkey}
\mailsa\\
\mailsc\\
\url{http://ceng.metu.edu.tr}

@@

% \toctitle{Lecture Notes in Computer Science}
% \tocauthor{Authors' Instructions}
% \maketitle
